Notes: New gaugings in 3d from three-form

### 2023-06-07 Draft_3dH3.tex
SUSY enhancement and metric zeta Omega.

The Ansätze~\eqref{eq:GSSansatz} describe a \textit{consistent} truncation if the following condition is satisfied:
\begin{equation} \label{eq:GenLeibniz}
	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M\,,
\end{equation}
with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor. This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
\begin{equation} \label{eq:GSSexample}
	\begin{aligned}
		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
	\end{aligned}
\end{equation}
where
\begin{equation} \label{eq:3dCovDeriv}
	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M})}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
\end{equation}

Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}. The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields. From eq. \eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
\begin{equation}
	\begin{aligned}
		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
	\end{aligned}
\end{equation}
Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=U_{\fl{M}}{}^{K}U_{\fl{N}}{}^{L}\partial_{K}U^{\fl{P}}{}_{L}$ and the trombone gauging
\begin{equation} \label{eq:Trombone}
	\begin{split}
		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
	\end{split}
\end{equation}
The embedding tensor is most nicely expressed once projected on the adjoint representation
\begin{equation} \label{eq:symembeddingtensor}
	\begin{aligned}
		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
	\end{aligned}
\end{equation}
with the projection of the current $\Gamma_{\fl{MN}} = - \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$. In the following, we will focus on gaugings with $\xi_{\fl{M}}=0$.

@@

Therefore, we can add a 7-form flux to the twist matrix using
\begin{equation}
	\cU_{\fl{M}}{}^M \longrightarrow \cU'_{\fl{M}}{}^M = \cU_{\fl{M}}{}^N \exp(C)_N{}^M \,,
\end{equation}
with $C_M{}^N = \lambda\, z\,\rho^{-1}\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux. The resulting embedding tensor is most nicely written using the branching
\begin{equation} \label{eq:248decompoinSL8}
	\begin{aligned}
		\EE & \longrightarrow E_{7(7)}\times {\rm SL}(2) \longrightarrow {\rm SL}(8) \times {\rm SL}(2) \\
		\mathbf{248} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
	,0);}\  (\mathbf{63},\mathbf{1}) \oplus (\mathbf{70},\mathbf{1}) \oplus (\mathbf{28},\mathbf{2}) \oplus (\mathbf{\fl{28}},\mathbf{2}) \oplus (\mathbf{1},\mathbf{3}) \\
		X^{\fl{M}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
	,0);}\ \left\{X^{\fl{\cal A}}{}_{\fl{\cal B}},X^{\fl{\cal ABCD}},X^{\fl{\cal AB}\,\fl{i}},X_{\fl{\cal AB}}{}^{\fl{i}},X^{\fl{\alpha}}\right\},
	\end{aligned}
\end{equation}
and has the following non-vanishing components:
\begin{equation} \label{eq:embeddingtensor@origin}
	\begin{aligned}
		X_{(\mathbf{63},\mathbf{1});(\mathbf{28},\mathbf{2})}:&
		\begin{cases}
			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I[K}}\delta_{\fl{L]}}{}^{\fl{J}},\\[7pt]
			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}},\\
		\end{cases} \\[5pt]
		X_{(\mathbf{63},\mathbf{1});(\mathbf{\fl{28}},\mathbf{2})}:&
		\begin{cases}
			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{\fl{[C}}\delta^{\fl{D]B}},\\[7pt]
			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}},\\
		\end{cases} \\[5pt]
		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};\fl{\alpha}} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}\,\delta_{\fl{\alpha}2},
	\end{aligned}
\end{equation}
with the component $\fl{\alpha} = 2$ of the adjoint of ${\rm SL}(2)$ corresponding to the generator $e = \begin{pmatrix} 0 & 1 \\ 0 & 0\end{pmatrix}$ in the basis $\fl{i}=\{+,-\}$. With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$. We fix this value in the following.

\EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
\EM{Vacuum condition for $\lambda$}\\
\EM{SUSY AdS$_3$ vacuum in 10-d}

\paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution ~\cite{deBoer:1999gea}
\begin{equation}
	\begin{aligned}
		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d z^{2},\\
		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right),
	\end{aligned}
\end{equation}
with $H_{(3)} = \d B_{(2)}$ and \CE{(with the normalization in eq.~\eqref{eq:3dpotential} and $\ell_{\rm AdS}^{2}=2/V_{0}$, the code gives an additional factor $1/2$)}
\begin{equation}
	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}.
\end{equation}
The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+1$. \CE{(add $S^{1}$ modulus here?)}

\paragraph{}
The 3d solution preserves ${\cal N}=(4,4)$ supercharges, with isometry group ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, \textit{i.e.} two copies of the large ${\cal N}=4$ supergroup. The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$. The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres. The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$). Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
\begin{equation} \label{eq:spectrumorigin}
	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}.
\end{equation}
In each factor the lowest conformal dimension is
\begin{equation}
	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}},
\end{equation}
with $n$ corresponding to the $S^{1}$ harmonics, and the lowest conformal dimension of $[\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}]$ is then
\begin{equation} \label{eq:confdims3s3s1}
	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}.
\end{equation}
 For $n=0$, the representations get shortened whenever $\ell = \ts{\ell}$. The spectrum at the consistent truncation is then the one of ref.~\cite{Hohm:2005ui}. It corresponds to $\ell=\ts{\ell}=n=0$ in eq.~\eqref{eq:spectrumorigin}:
 \begin{equation}
 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \oplus [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
 \end{equation}
 The first two terms build the supergravity multiplet, each of them carrying one spin-2 field, four gravitini, seven vectors and four spin-$\nicefrac{1}{2}$ fields, all massless. The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in the tab.~4 of ref.~\cite{Hohm:2005ui}). \CE{(give these details here?)}

@@

This deformation breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. Concerning the spectrum, the conformal dimension of each field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation}
	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm R}+q_{\rm L})\,\chi_{1}+(q_{\rm R}-q_{\rm L})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm R}+\ts{q}_{\rm L})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm L}-\ts{q}_{\rm R})\,\ts{\chi}_{2}\Big),
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$. \CE{(Issue here!)}

\CE{(Discuss SUSY enhancement)}

>>>>

The Ansätze~\eqref{eq:GSSansatz} describe a \textit{consistent} truncation if the following condition is satisfied:
\begin{equation} \label{eq:GenLeibniz}
	\gL_{\ff{U}_{\fl{M}}} {\cU}_{\fl{N}}{}^M = X_{\fl{M}\fl{N}}{}^{\fl{P}}\, \cU_{\fl{P}}{}^M\,,
\end{equation}
with $\cU_{\fl{M}}{}^M = \rho^{-1} \UI_{\fl{M}}{}^M$, $\ff{U}_{\fl{M}} = (\cU_{\fl{M}},\,\Sigma_{\fl{M}})$ and $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ a constant tensor. This condition ensures that the factorised form of the Ansätze~\eqref{eq:GSSansatz} is preserved by the generalized Lie derivative, \textit{e.g.}
\begin{equation} \label{eq:GSSexample}
	\begin{aligned}
		D_{\mu}\M(x,Y) &= U_{M}{}^{\fl{M}}(Y)\,U_{N}{}^{\fl{N}}(Y)\,{\cal D}_{\mu}\M_{\fl{MN}}(x)\,,\\
		{\cal L}_{(A_{\mu},B_{\nu})}A_{\mu}(x,Y) &= \rho(Y)^{-1}\,\UI_{\fl{M}}{}^{M}(Y)\,\llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}(x)\,,
	\end{aligned}
\end{equation}
where
\begin{equation} \label{eq:3dCovDeriv}
	{\cal D}_{\mu}\M_{\fl{MN}} = \partial_{\mu}\M_{\fl{MN}}-2\,\A_{\mu}{}^{\fl{P}}X_{\fl{P}(\fl{M}}{}^{\fl{Q}}\M_{\fl{N})\fl{Q}}\,, \quad {\rm and} \quad \llbracket\A_{\mu},\A_{\nu}\rrbracket^{\fl{M}}=X_{\fl{PQ}}{}^{\fl{M}}\A_{\mu}{}^{\fl{P}}\A_{\nu}^{\fl{Q}} \,.
\end{equation}

Thus, for a given twist matrix $U_{M}{}^{\fl{M}}$ satisfying the consistency condition~\eqref{eq:GenLeibniz}, the action~\eqref{eq:ExFTaction} reduces to three-dimensional ${\cal N}=16$ gauged supergravity \cite{Nicolai:2000sc,Nicolai:2001sv}. The constant tensor $X_{\fl{M}\fl{N}}{}^{\fl{P}}$ plays the role of the embedding tensor of the three-dimensional gauged supergravity, as is clear from its appearance in \eqref{eq:3dCovDeriv} in the gauge-covariant derivative and the gauge algebra of the vector fields. From eq. \eqref{eq:GenLeibniz}, it has the following expression in terms of the twist matrix and $\rho$
\begin{equation}
	\begin{aligned}
		X_{\fl{MN}}{}^{\fl{P}}&=-\rho^{-1}\,\Gamma_{\fl{MN}}{}^{\fl{P}} + \rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{L}}\,\Gamma_{\fl{KM}}{}^{\fl{L}}-\frac{1}{60}\,\rho^{-1}\,f^{\fl{PK}}{}_{\fl{N}}\,f_{\fl{ML}}{}^{\fl{Q}}\,\Gamma_{\fl{KQ}}{}^{\fl{L}}\\
		&\quad-\frac{1}{2}\,\rho^{-1}\,f^{\fl{P}}{}_{\fl{NQ}}\,f^{\fl{QK}}{}_{\fl{M}}\,\Gamma_{\fl{RK}}{}^{\fl{R}}+\left(\delta_{\fl{M}}{}^{\fl{K}}\delta_{\fl{N}}{}^{\fl{P}}-\frac{1}{2}\,f_{\fl{M}}{}^{\fl{LK}}f_{\fl{NL}}{}^{\fl{P}}\right)\,\xi_{\fl{K}}\,.
	\end{aligned}
\end{equation}
Here, we defined the ${\rm E}_{8(8)}$ current $\Gamma_{\fl{MN}}{}^{\fl{P}}=\UI_{\fl{M}}{}^{K}\UI_{\fl{N}}{}^{L}\partial_{K}U_{L}{}^{\fl{P}}$ and the trombone gauging
\begin{equation} \label{eq:Trombone}
	\begin{split}
		\xi_{\fl{M}} %&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1}+\rho^{-1}\,\partial_{N}U_{\fl{M}}{}^{N} \\
		&= 2\,U_{\fl{M}}{}^{N}\partial_{N}\rho^{-1} - \rho^{-1}\, \Gamma_{\ov{N}\ov{M}}{}^{\ov{N}} \,.
	\end{split}
\end{equation}
The embedding tensor is most nicely expressed once projected on the adjoint representation
\begin{equation} \label{eq:symembeddingtensor}
	\begin{aligned}
		X_{\fl{MN}} = -\frac{1}{60}\,X_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}} &= - 2\,\rho^{-1}\,\Gamma_{(\fl{MN})} - \rho^{-1}\,\Gamma_{\fl{P}(\fl{M}}{}^{\fl{Q}}\,f_{\fl{N})\fl{Q}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \\
		&= - 14\,\rho^{-1}\,(\mathbb{P}_{3875})_{\fl{MN}}{}^{\fl{PQ}}\,\Gamma_{\fl{PQ}} - \frac{1}{4}\,\rho^{-1}\,\eta_{\fl{MN}}\,\Gamma_{\fl{P}}{}^{\fl{P}} + \frac12 f_{\ov{M}\ov{N}}{}^{\ov{P}}\, \xi_{\ov{P}} \,,
	\end{aligned}
\end{equation}
with the projection of the current $\Gamma_{\fl{MN}} = - \tfrac{1}{60}\,\Gamma_{\fl{MP}}{}^{\fl{Q}}\,f_{\fl{NQ}}{}^{\fl{P}}$. In the following, we will focus on gaugings with $\xi_{\fl{M}}=0$.

@@

Therefore, we can add a 7-form flux to the twist matrix using
\begin{equation}
	\cU_{\fl{M}}{}^M \longrightarrow \cU'_{\fl{M}}{}^M = \cU_{\fl{M}}{}^N \exp(C)_N{}^M \,,
\end{equation}
with $C_M{}^N = \lambda\, z\,\rho^{-1}\, t_{1238\,M}{}^N$ and $\lambda$ a numerical parameter corresponding to the amount of 7-form flux. The resulting embedding tensor is most nicely written using the branching
\begin{equation} \label{eq:248decompoinSL8}
	\begin{aligned}
		\EE & \longrightarrow E_{7(7)}\times {\rm SL}(2) \longrightarrow {\rm SL}(8) \times {\rm SL}(2) \\
		\mathbf{248} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
	,0);}\  (\mathbf{63},\mathbf{1}) \oplus (\mathbf{70},\mathbf{1}) \oplus (\mathbf{28},\mathbf{2}) \oplus (\mathbf{\fl{28}},\mathbf{2}) \oplus (\mathbf{1},\mathbf{3}) \\
		X^{\fl{M}} & \ \tikz{\draw[arrows={->[scale=1.1]}] (0,0) -- (3.65
	,0);}\ \left\{X^{\fl{\cal A}}{}_{\fl{\cal B}},X^{\fl{\cal ABCD}},X^{\fl{\cal AB}\,\fl{i}},X_{\fl{\cal AB}}{}^{\fl{i}},X^{\fl{\alpha}}\right\},
	\end{aligned}
\end{equation}
and has the following non-vanishing components:
\begin{equation} \label{eq:embeddingtensor@origin}
	\begin{aligned}
		X_{(\mathbf{63},\mathbf{1});(\mathbf{28},\mathbf{2})}:&
		\begin{cases}
			\displaystyle X_{\fl{I}}{}^{\fl{J}}{}_{;\fl{KL}+}=-\frac{1}{\alpha}\,\delta_{\fl{I}[\fl{K}}\delta_{\fl{L}]}{}^{\fl{J}},\\[7pt]
			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;\fl{BJ}+}=-\frac{1}{2\alpha}\,\delta_{\fl{AB}}\delta_{\fl{J}}{}^{\fl{I}},\\
		\end{cases} \\[5pt]
		X_{(\mathbf{63},\mathbf{1});(\mathbf{\fl{28}},\mathbf{2})}:&
		\begin{cases}
			\displaystyle X_{\fl{A}}{}^{\fl{B}}{}_{;}{}^{\fl{CD}}{}_{+}=-\,\delta_{\fl{A}}{}^{[\fl{C}}\delta^{\fl{D}]\fl{B}},\\[7pt]
			\displaystyle X_{\fl{A}}{}^{\fl{I}}{}_{;}{}^{\fl{BJ}}{}_{+}=-\frac{1}{2}\,\delta_{\fl{A}}{}^{\fl{B}}\delta^{\fl{IJ}},\\
		\end{cases} \\[5pt]
		X_{(\mathbf{70},\mathbf{1});(\mathbf{1},\mathbf{3})}:&\  X_{\fl{IJKL};++} = -\frac{\lambda}{12\sqrt{6}}\,\varepsilon_{\fl{IJKL}}.
	\end{aligned}
\end{equation}
With this embedding tensor, the potential~\eqref{eq:3dpotential} is stabilized at the scalar origin for $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$. We fix this value in the following.

% \EM{Give embedding tensor components wrt the 3-d basis used for the moduli}\\
% \EM{Vacuum condition for $\lambda$}\\
% \EM{SUSY AdS$_3$ vacuum in 10-d}

\paragraph{} At $\lambda=4\sqrt{3}\,\sqrt{1+(1/\alpha^{2})}$, the three-dimensional solution described by the embedding tensor~\eqref{eq:embeddingtensor@origin} corresponds to the consistent truncation of the pure NSNS ten-dimensional solution~\cite{deBoer:1999gea}
\begin{equation}
	\begin{aligned}
		\d s^{2} &= \ell_{\rm AdS}^{2}\,\d s^{2}\left({\rm AdS}_{3}\right) + \alpha^{2}\,\d s^{2}\big(S^{3}\big)+\d s^{2}\big(\ts{S}^{3}\big)+\d z^{2},\\
		H_{(3)} &= 2\left(\ell_{\rm AdS}^{2}\,{\rm Vol}({\rm AdS_{3}})+\alpha^{2}\,{\rm Vol}\big(S^{3}\big)+{\rm Vol}\big(\ts{S}^{3}\big)\right),
	\end{aligned}
\end{equation}
with $H_{(3)} = \d B_{(2)}$ and
\begin{equation}
	\ell_{\rm AdS}^{2} = \frac{\alpha^{2}}{1+\alpha^{2}}.
\end{equation}
The $S^{1}$ coordinate $z$ has periodicity $z\rightarrow z+2\pi$.

\paragraph{}
The 3d solution preserves ${\cal N}=(4,4)$ supercharges, with isometry group ${\cal G}=D^{1}(2,1;\alpha)_{\rm L}\times D^{1}(2,1;\alpha)_{\rm R}$, \textit{i.e.} two copies of the large ${\cal N}=4$ supergroup. The even part of $D^{1}(2,1;\alpha)$ is isomorphic to ${\rm SL}(2,\mathbb{R})\times{\rm SO}(3)\times\ts{{\rm SO}(3)}$ and the bosonic isometries of the ${\rm AdS}_{3}\times S^{3}\times\ts{S}^{3}$ background are built from the even part of ${\cal G}$. The ${\rm AdS}_{3}$ isometry group is ${\rm SO}(2,2)\simeq{\rm SL}(2,\mathbb{R})_{\rm L}\times{\rm SL}(2,\mathbb{R})_{\rm R}$, and the factors ${\rm SO}(3)_{\rm L}\times{\rm SO}(3)_{\rm R}\times\ts{{\rm SO}(3)}_{\rm L}\times\ts{{\rm SO}(3)}_{\rm R}\simeq{\rm SO}(4)\times\ts{SO(4)}$ combine into the isometry groups of the two spheres. The spectrum organizes into multiplets of ${\cal G}$, made out of products of long representations $[\ell,\ts{\ell}]$ of $D^{1}(2,1;\alpha)$ (see app.~\ref{app:d21a} for a review of the representations of $D^{1}(2,1;\alpha)$). Explicitly, the spectrum is~\cite{Eberhardt:2017fsi}
\begin{equation} \label{eq:spectrumorigin}
	\bigoplus_{\ell,\ts{\ell}\geq0} [\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}] \ \ominus\ [0,0]_{\rm s} \otimes [0,0]_{\rm s}.
\end{equation}
In each factor the lowest conformal dimension is
\begin{equation}
	h_{\rm L} = h_{\rm R} = -\frac{1}{2} + \frac{1}{2}\sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}},
\end{equation}
with $n$ corresponding to the $S^{1}$ harmonics, and the lowest conformal dimension of $[\ell,\ts{\ell}]\otimes[\ell,\ts{\ell}]$ is then
\begin{equation} \label{eq:confdims3s3s1}
	\Delta_{\ell,\,\ts{\ell},\,n} = h_{\rm L} + h_{\rm R} = - 1 + \sqrt{1+\frac{4\,\ell(\ell+1)+4\,\alpha^{2}\,\ts{\ell}(\ts{\ell}+1)+(2\pi n)^{2}}{1+\alpha^{2}}}.
\end{equation}
 For $n=0$, the representations get shortened whenever $\ell = \ts{\ell}$. The spectrum at the consistent truncation is then the one of ref.~\cite{Hohm:2005ui}. It corresponds to $\ell=\ts{\ell}=n=0$ in eq.~\eqref{eq:spectrumorigin}:
 \begin{equation} \label{eq:CTmultorigin}
 	[0,0]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [0,0]_{\rm s} \ \oplus \ [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s} \otimes [\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}.
 \end{equation}
 The first two terms build the supergravity multiplet, each of them carrying one spin-2 field, four gravitini, seven vectors and four spin-$\nicefrac{1}{2}$ fields, all massless. The only propagating degrees of freedom are in $[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}\otimes[\nicefrac{1}{2},\nicefrac{1}{2}]_{\rm s}$ (see the details in the tab.~4 of ref.~\cite{Hohm:2005ui}).

@@

This deformation breaks $\SO{3}_{\rm L}\times\SO{3}_{\rm R}\times\ts{\SO{3}}_{\rm L}\times\ts{\SO{3}}_{\rm R}$ to ${\rm U}(1)_{\rm L}\times{\rm U}(1)_{\rm R}\times\ts{{\rm U}(1)}_{\rm L}\times\ts{{\rm U}(1)}_{\rm R}$ and all supersymmetries. Concerning the spectrum, the conformal dimension of each physical field (\textit{c.f.} eq.~\eqref{eq:confdims3s3s1}) get shifted by replacing
\begin{equation} \label{eq:confdimshiftchi}
	2\pi n\longrightarrow \frac{2\pi n}{T} + \frac{1}{2T}\Big((q_{\rm L}+q_{\rm R})\,\chi_{1}+(q_{\rm L}-q_{\rm R})\,\chi_{2}+ \alpha\,(\ts{q}_{\rm L}+\ts{q}_{\rm R})\,\ts{\chi}_{1}+ \alpha\,(\ts{q}_{\rm R}-\ts{q}_{\rm L})\,\ts{\chi}_{2}\Big),
\end{equation}
where the $q$ denote the charges under the different ${\rm U}(1)$.
